Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd

@@

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, out.width="200px"}
library(magrittr)
library(ggplot2)
library(dplyr)
df2 <- df0 %>% group_by(publication_decade, catalog) %>%
               summarise(n = n())
df2$highlight <- rep(FALSE, nrow(df2))
df2$highlight[df2$catalog == "Kungliga" &
	      df2$publication_decade %in% c(1770, 1810)] <- TRUE
df2$highlight[df2$catalog == "Fennica" &
	      df2$publication_decade %in% c(1710, 1810)] <- TRUE
v <- seq(1500, 1800, 50)
theme_set(theme_bw(20))
p <- ggplot(df2, aes(x = publication_decade, y = n)) +
     geom_line(aes(group = catalog), color = "black") +
     #geom_smooth(aes(fill = catalog)) + 
     geom_point(aes(shape = catalog, color = highlight, size = highlight)) +
     ylab("Title count (n)") + xlab("Publication year") +
     scale_color_manual(values = c("black", "black")) +
     #scale_color_manual(values = c("black")) +
       theme(legend.position = "none") +
     scale_x_continuous(breaks = v, labels = v)
     # ggtitle("Overall publishing activity")
print(p)
```

>>>>

### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828

1) General trends & political events

2) Publishers in Sweden and Turku

3) Languages & religious texts in Finland

4) University curriculum & Enlightenment in Finland

Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.

@@

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, out.width="200px"}
library(magrittr)
library(ggplot2)
library(dplyr)
df2 <- df0 %>% group_by(publication_decade, catalog) %>%
               summarise(n = n())
df2$highlight <- rep(FALSE, nrow(df2))
df2$highlight[df2$catalog == "Kungliga" &
	      df2$publication_decade %in% c(1770, 1810)] <- TRUE
df2$highlight[df2$catalog == "Fennica" &
	      df2$publication_decade %in% c(1710, 1810)] <- TRUE
v <- seq(1500, 1800, 50)
theme_set(theme_bw(20))
p <- ggplot(df2, aes(x = publication_decade, y = n)) +
     geom_line(aes(color = catalog), size = 1) +
     geom_point(aes(shape = catalog, color = highlight, size = highlight)) +
     ylab("Title count (n)") + xlab("Publication year") +
     #theme(legend.position = "none") +
     scale_x_continuous(breaks = v, labels = v) +
     scale_color_manual(values = c("black", "blue", "darkgreen", "blue")) + 
     guides(fill = guide_legend(reverse = TRUE)) 
print(p)
```
